---
# Copyright (c) 2018-2019 Intel Corporation
#
# SPDX-License-Identifier: Apache-2.0
#
---
\pagebreak

# Introduction
This report compares the metrics between multiple sets of data generated from
the [cloud-native-setup report generation scripts](https://github.com/clearlinux/cloud-native-setup/metrics/report/README.md).

This report was generated using the data from the **`r resultdirs`** results directories.

\pagebreak

# Runtime scaling
This [test](https://github.com/clearlinux/cloud-native-setup/metrics/scaling/k8s_scale.sh)
measures the system memory 'free' reduction, CPU idle %, free inodes, and pod boot time as
it launches more and more idle `busybox` pods on a Kubernetes cluster.

> Note: CPU % is measured as a system whole - 100% represents *all* CPUs on the node.

```{r scaling, echo=FALSE, fig.cap="K8S scaling", results='asis'}
source('tidy_scaling.R')
```

\pagebreak

# Runtime parallel scaling
This [test](https://github.com/clearlinux/cloud-native-setup/metrics/scaling/k8s_parallel.sh)
measures the time taken to launch and delete pods in parallel using a deployment. The times
are how long it takes for the whole deployment operation to complete.

```{r parallel, echo=FALSE, fig.cap="K8S parallel pods", results='asis'}
source('parallel.R')
```

\pagebreak

# Runtime scaling rapid
This [test](https://github.com/clearlinux/cloud-native-setup/metrics/scaling/k8s_scale_fast.sh)
uses collectd to asynchronously measure CPU idle %, free memory, pod boot time, free inodes,
and interface stats as it launches more and more idle `busybox` pods on a Kubernetes cluster.

> Note: CPU % is measured as a system whole - 100% represents *all* CPUs on the node.

```{r collectd, echo=FALSE, fig.cap="K8S scaling collectd", results='asis'}
source('collectd_scaling.R')
```

\pagebreak

# Pod communication latency
This [test](https://github.com/clearlinux/cloud-native-setup/metrics/scaling/k8s_scale_rapid_nc.sh)
measures pod query--response latency when scaling up. The
time is measured from sending a message directly to a socket, that `nc`
listens to inside each pod, to reading the response from the pod.

```{r scaling_nc, echo=FALSE, fig.cap="K8S pod communication latency", results='asis'}
source('tidy_scaling_nc.R')
```

\pagebreak

# Test setup details

This table describes the test system details, as derived from the information contained
in the test results files.


```{r dut, echo=FALSE, fig.cap="System configuration details", results='asis'}
source('dut-details.R')
```

\pagebreak

# Test setup node details

This table describes node details within the Kubernetes cluster that have been used for test.

```{r node, echo=FALSE, fig.cap="Node information within Kubernetes cluster", results='asis'}
source('node-info.R')
```
